Procedural generation of levels for the angry birds videogame using evolutionary computation\\

### 2019-05-15 IEEE_ConferenceOnGames/new_article.tex
about to start second edit
Change to explanations
Section description on "Introduction" section & section description on section 3

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

    Section 2, contains a quick overview of some aspects used by different authors
    in order to tackle this problem, their design and basic functionality, in
    Section 3 the description of the current state of the project is explained, from
    %% The following sentence is not clear.
    the way the candidate solutions are represented, to the way the mutations are applied 
    to them, as well as the way we use our fitness function to determine the playability
    and complexity of the generated levels, 
    finally in Section 4 we provide our conclusions about the development of this
    paper as well as improvements that can help to refine the proposed work.

@@

    \section{Proposed Method}

    In this Section we describe the approach used in this work, explaining first,
    the restrictions of the game.
    The game contains a total of 11 block shapes as shown in Figure \ref{piece_list}.
    These basic blocks cannot be modified, it is not possible to add more or modify the existing ones,
    with this in mind the purpose is to create composites of these blocks in
    different locations and angles in order to create structures that can be used as
    building blocks for more complex structures.

@@

    \section{Conclusions and future work}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

    Section \ref{SoA}, contains a quick overview of some aspects used by different authors
    in order to tackle this problem, their design and basic functionality, in
    Section \ref{prop_method} the description of the current state of the project is explained, how
    %% The following sentence is not clear.  % Maybe this modofocation is more understandable ? JSH
    the candidate solutions are represented and the way we defined our fitness 
    function to determine the playability and complexity of the generated levels, 
    finally in Section \ref{conclusion} we provide our conclusions about the development of this
    paper as well as improvements that can help to refine the proposed work.

@@

    \section{Proposed Method}
    \label{prop_method}

    % Is this explanation undertandable ? JSH
    In this section we describe the approach used in this work, explaining first,
    the restrictions of the game, then giving a quick overview of how we create new 
    composites to be used by the algorithm, then explaining how the candidate solutions 
    are represented and how this are modified and evolved by the algorithm, and finally 
    we present our method to evaluate the candidate solutions.

    The game contains a total of 11 block shapes as shown in Figure \ref{piece_list}.
    These basic blocks cannot be modified, it is not possible to add more or modify the existing ones,
    with this in mind the purpose is to create composites of these blocks in
    different locations and angles in order to create structures that can be used as
    building blocks for more complex structures.

@@

    \section{Conclusions and future work}
    \label{conclusion}
